

---
title: "Case Study 1"
author: "Murtada Shubbar"
date: "June 30, 2017"
output:
  html_document:
    keep_md: true
---
knitr::opts_chunk$set(echo = TRUE) 

Data Analysis: Murtada Shubbar
 
The data analyzed in this case study summarizes and visualizes two data sets, 
craft beers and breweries from the United States. Included in the data is a list of 
2410 beer variations and 557 breweries from all 51 States. The data also includes the 
following: City, Names, IDs, Alcohol by Volume (ABV), International Bitterness Unit (IBU),etc. z

After merging the data, we will be computing the median alcohol content and IBU for
each state, identifying which state has the maximum alcoholic beer and bitterness, 
summarize ABV, and find relationships between bitterness and alcoholic content.
Some visual aids such (plots) will be accompanying the data for further clarification. 


#################################################################
```{r proof1}
R.version 
```

```{r proof22}
library(ggplot2)
library(plyr)
```

setwd("C:\\Users\\Murtada\\Desktop\\SMU DATA SCIENCE\\2017 MAY TERM\\Doing Data Science\\CASE STUDY 1\\GitHub\\CaseStudy1")

```{r proof2}
beers<- read.csv("C:\\Users\\Murtada\\Desktop\\SMU DATA SCIENCE\\2017 MAY TERM\\Doing Data Science\\CASE STUDY 1\\GitHub\\RawData\\Beers.csv")
breweries<- read.csv("C:\\Users\\Murtada\\Desktop\\SMU DATA SCIENCE\\2017 MAY TERM\\Doing Data Science\\CASE STUDY 1\\GitHub\\RawData\\Breweries.csv")
```


Question 1
The following displays how many breweries are present in each state.
We have states like WV, SD, DC that have one brewery and other heavy
hitters like CA, MI, and CO. The code bellow elegantly uses the variable
to summarize how many breweries are in in the data set. 

```{r prof3}
summary(breweries$State)
```


Question 2 
As we can see, the two data sets are merged bellow by the brewery id. 
The first and last 6 observations are printed to verify the merging. 
The merge function is used to merge both data sets and the head/tail
function is used to display the first 6 and last 6 observations. 


```{r prof4}
Merg<-merge(x=breweries, y=beers, by.x="Brew_ID", by.y="Brewery_id", all=TRUE)
#####################First 6 Observations
head(Merg)
#####################Last 6 Observations 
tail(Merg)
```


Question 3 
The number of NA's in each column are as following: 
In ABV there are 62 NA's. 
in IBU there are 1005 NA's

```{r prof5}
colSums(is.na(Merg))
```


Question 4 
The following computes the median alcohol content and international
bitterness unit for each state. The bar graph is a visual representation of the data. 

```{r prof6}
MedABV <- aggregate(ABV ~State, data =Merg, FUN = median)
MedIBU <- aggregate(IBU ~State, data =Merg, FUN = median)
```

```{r, echo=TRUE}

ggplot(data = MedABV,aes(State, ABV,fill=ABV)) +geom_bar(color="black",stat = "identity")+theme(text=element_text(size=15))
```

```{r, echo=TRUE}
ggplot(data = MedIBU,aes(State, IBU,fill=IBU)) +geom_bar(color="black",stat = "identity")+theme(text=element_text(size=15))
```


Question 5
From the following analysis we have determined Colorado has the maximum alcoholic beer. 
Also from the same analysis we have determined Oregon has the most bitter beer. 

```{r prof7}
Merg[which.max(Merg$ABV),]
Merg[which.max(Merg$IBU),]
```


Question 6
The following displays the summary statistics for the ABV variable: 

```{r prof8}
summary(Merg$ABV)
```

Question 7 
The following displays the relationship between the bitterness of the beer 
and its alcoholic content using a scatter plot: 

```{r, echo=TRUE}
Scattergraph <- ggplot(Merg, aes(IBU, ABV, label = State)) + geom_point(shape=1) +
  geom_smooth(method = lm) 
Scattergraph
```

As the positive slope indicates, it appears that the more alcoholic the beer is, the more bitter it becomes. 


























